---
title: "Simulations_decision_making"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Prepare packages and functions
```{r}
setwd("/work/Exam/decision_making")
source("simulation.r")
# install.packages("pacman")
library(pacman)
p_load(tidyverse, network, igraph, intergraph, tidygraph, ggraph, ggplot2, ggthemes)
```

The defaults of the function is 
n = 10000 (10000 nodes)
nei = 2 (gives a baseline neighborhood of 12)
tau_type = "random_tau" (meaning that thresholds are normally distributed)
tau = 0.33 (sd = 0.16 hardcoded in the function)
rep = 100
rounds = 100

In the following, simulations using 50, 100 and 150 initially seeded nodes is used. 
When highly influential (high status or degree) nodes are included, they are also the initial seeds. 

Baseline model
```{r}
# baseline2 <- contagion_sim(n_seeds = 2)
# baseline4 <- contagion_sim(n_seeds = 4)
# baseline8 <- contagion_sim(n_seeds = 8)
```

High status nodes - percentage = 1
```{r}
# high_status2_perc1 <- contagion_sim(n_seeds = 2,
                                     n_high = 2,
                                     high_status = TRUE,
                                     high_tau_perc = 1)

# high_status4_perc1 <- contagion_sim(n_seeds = 4,
                                      n_high = 4,
                                      high_status = TRUE,
                                      high_tau_perc = 1)

high_status8_perc1 <- contagion_sim(n_seeds = 8,
                                      n_high = 8,
                                      high_status = TRUE,
                                      high_tau_perc = 1)
print("Finished High status nodes - percentage = 1")
```

High status nodes - percentage = 0.75
```{r}
high_status2_perc075 <- contagion_sim(n_seeds = 2,
                                       n_high = 2,
                                       high_status = TRUE,
                                       high_tau_perc = 0.75)

high_status4_perc075 <- contagion_sim(n_seeds = 4,
                                        n_high = 4,
                                        high_status = TRUE,
                                        high_tau_perc = 0.75)

high_status8_perc075 <- contagion_sim(n_seeds = 8,
                                        n_high = 8,
                                        high_status = TRUE,
                                        high_tau_perc = 0.75)
print("Finished High status nodes - percentage = 0.75")
```

High status nodes - percentage = 0.5
```{r}
high_status2_perc05 <- contagion_sim(n_seeds = 2,
                                      n_high = 2,
                                      high_status = TRUE,
                                      high_tau_perc = 0.5)

high_status4_perc05 <- contagion_sim(n_seeds = 4,
                                       n_high = 4,
                                       high_status = TRUE,
                                       high_tau_perc = 0.5)

high_status8_perc05 <- contagion_sim(n_seeds = 8,
                                       n_high = 8,
                                       high_status = TRUE,
                                       high_tau_perc = 0.5)
print("Finished High status nodes - percentage = 0.5")
```

High degree nodes - degree = 24
```{r}
high_degree2_n_con24 <- contagion_sim(n_seeds = 2,
                                       n_high = 2,
                                       high_degree = TRUE,
                                       connectedness = 24)

high_degree4_n_con24 <- contagion_sim(n_seeds = 4,
                                        n_high = 4,
                                        high_degree = TRUE,
                                        connectedness = 24)

high_degree8_n_con24 <- contagion_sim(n_seeds = 8,
                                        n_high = 8,
                                        high_degree = TRUE,
                                        connectedness = 24)
print("Finished High degree nodes - degree = 24")
```

High degree nodes - degree = 48
```{r}
high_degree2_n_con48 <- contagion_sim(n_seeds = 2,
                                       n_high = 2,
                                       high_degree = TRUE,
                                       connectedness = 48)

high_degree4_n_con48 <- contagion_sim(n_seeds = 4,
                                        n_high = 4,
                                        high_degree = TRUE,
                                        connectedness = 48)

high_degree8_n_con48 <- contagion_sim(n_seeds = 8,
                                        n_high = 8,
                                        high_degree = TRUE,
                                        connectedness = 48)
print("Finished High degree nodes - degree = 48")
```

High degree nodes - degree = 96
```{r}
high_degree2_n_con96 <- contagion_sim(n_seeds = 2,
                                       n_high = 2,
                                       high_degree = TRUE,
                                       connectedness = 96)

high_degree4_n_con96 <- contagion_sim(n_seeds = 4,
                                        n_high = 4,
                                        high_degree = TRUE,
                                        connectedness = 96)

high_degree8_n_con96 <- contagion_sim(n_seeds = 8,
                                        n_high = 8,
                                        high_degree = TRUE,
                                        connectedness = 96)
print("Finished High degree nodes - degree = 96")
```

