---
title: "Simulations_decision_making"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Prepare packages and functions
```{r}
# setwd("/work/Exam/decision_making")
source("functions/simulation.r")
# install.packages("pacman")
library(pacman)
p_load(tidyverse, network, igraph, intergraph, tidygraph, ggraph, ggplot2, ggthemes)
```

The defaults of the function is 
n = 3600 (3600 nodes)
nei = 2 (gives a baseline neighborhood of 12)
tau_type = "random_tau" (meaning that thresholds are normally distributed)
tau = 0.33 (sd = 0.16 hardcoded in the function)
rep = 50
rounds = 50

In the following, simulations using 0.5% and 1% high status nodes is used. 
When highly influential (high status or degree) nodes are included, they are also the initial seeds. 


```{r}
# Baseline 
# contagion_sim()

# High status nodes - percentage = 1 - Stine
contagion_sim(n_high = 36, 
              high_status = TRUE, 
              high_tau_perc = 1)

contagion_sim(n_high = 18,
              high_status = TRUE,
              high_tau_perc = 1)

# High status nodes - percentage = 0.75 - Stine
contagion_sim(n_high = 36,
              high_status = TRUE,
              high_tau_perc = 0.75)

contagion_sim(n_high = 18,
              high_status = TRUE,
              high_tau_perc = 0.75)

# High status nodes - percentage = 0.5
contagion_sim(n_high = 36,
              high_status = TRUE,
              high_tau_perc = 0.5)

contagion_sim(n_high = 18,
              high_status = TRUE,
              high_tau_perc = 0.5)

```


```{r}
# High degree nodes - degree = 24

contagion_sim(n_high = 36,
              high_degree = TRUE,
              connectedness = 24)
```


```{r}
contagion_sim(n_high = 18,
              high_degree = TRUE,
              connectedness = 24)

print("Finished High degree nodes - degree = 24")
```


```{r}
#High degree nodes - degree = 48

contagion_sim(n_high = 36,
              high_degree = TRUE,
              connectedness = 48)

contagion_sim(n_high = 18,
              high_degree = TRUE,
              connectedness = 48)


print("Finished High degree nodes - degree = 48")
```


```{r}
# High degree nodes - degree = 96

contagion_sim(n_high = 36,
              high_degree = TRUE,
              connectedness = 96)
```


```{r}
contagion_sim(n_high = 18,
              high_degree = TRUE,
              connectedness = 96)

print("Finished High degree nodes - degree = 96")

```


### POST HOC ###
```{r}
contagion_sim(n_high = 72,
              high_status = TRUE,
              high_tau_perc = 1)

contagion_sim(n_high = 144,
              high_status = TRUE,
              high_tau_perc = 1)

contagion_sim(n_high = 288,
              high_status = TRUE,
              high_tau_perc = 1)

```


```{r}
contagion_sim(n_high = 72,
              high_degree = TRUE,
              connectedness = 48)

contagion_sim(n_high = 144,
              high_degree = TRUE,
              connectedness = 48)

contagion_sim(n_high = 72,
              high_degree = TRUE,
              connectedness = 24)

contagion_sim(n_high = 144,
              high_degree = TRUE,
              connectedness = 24)

contagion_sim(n_high = 288,
              high_degree = TRUE,
              connectedness = 24)

```

Large network
```{r}
#High status
# 2% high status nodes
contagion_sim(n=22500, n_high=450, high_status=T, high_tau_perc=1)

# 4% high status nodes
contagion_sim(n=22500, n_high=900, high_status=T, high_tau_perc=1)
```

```{r}
#High degree
# 2% high status nodes
contagion_sim(n=22500, n_high=450, high_degree = T, connectedness = 24)
```

```{r}
# 4% high status nodes
contagion_sim(n=22500, n_high=900, high_degree = T, connectedness = 24)

```







